Imprecise Computing in Datapath Design: An Overclocking Approach

### 2013-05-09 TCAD2013/overclocking_tcad.tex
Modified several Figures: CSA and FIR

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
%
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
%
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
%
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
%
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
%for IEEE journal papers produced under \LaTeX\ using
%IEEEtran.cls version 1.8 and later.
%% You must have at least 2 lines in the paragraph with the drop letter
%I wish you the best of success.

\IEEEPARstart{C}{ircuit} performance has increased tremendously over the past decades, as CMOS technology continues to shrink to the nanometer regime. However, the drastic variations introduced by higher integration densities is anticipated to be the major obstacle when designing reliable, high performance circuits. Traditionally, hardware designers employ safety margins to ensure a uniform functionality across a variety of possible working environments. However, there are two major problems if we keep using this approach. One is that the uniform performance should no longer be expected in the future, because the highly scaled CMOS devices would inevitably exhibit probabilistic behavior. The other problem is that covering all possible worst cases would become increasingly difficult, expensive and result in large yield loss.

In addition, we also notice that the clock frequency is no longer scaling significantly with time, and the dark silicon becomes an important issue in circuit design since energy efficiency is considered to be the main limitation for embedded or mobile applications~\cite{FutureMicroprocessor2005,DarkSilicon2011}. In this case, designers tend to employ multi-core systems, heterogeneous platforms and massive parallel accelerators (such as FPGAs) to sustain the performance scaling.

Specifically, large volume of current studies has demonstrated that, significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications. However, one of the major factors that limits the performance of these accelerators is that they typically run at much lower clock frequencies than general purpose processors (GPPs) or GPUs. Furthermore, timing analysis tools typically report a very conservative clock frequency for ``safe'' operations. This substantially limits the potential performance of the device to a further extent.

In order to boost the operating frequency of a datapath, the standard approaches are either to heavily pipeline the design, or reduce the precision throughout the datapath. For the former method, pipelining will not tend to reduce the circuit latency. Actually the latency in terms of clock cycles will increase. As a result, this method will not be applicable to many embedded applications, which typically have strict latency requirements, or in datapath containing feedback where C-slow retiming is inappropriate. For the second approach, reducing the datapath precision would subtract out the latency, but at the cost of introducing quantization errors into the design. For hardware platforms such as FPGAs or ASICs, research into exploiting the potential benefits of using the minimum precision necessary to satisfy a design specification has been an extensive topic~\cite{GeorgeDT11}, as it is possible to use a number system with customized precisions on these platforms. A brief review of existing approaches in this area will be discussed in Section~\ref{Section_Background_WL}.

Unfortunately, neither of the conventional approaches tends to remove the conservative safety margin. In recent years, we have seen a growth of research that explores the potential power or performance benefits that can be obtained when relaxing the variation-induced guard-bands~\cite{NewBox2004}. The detailed review of this research area will be presented in Section~\ref{Section_Background_Imprecise}.

In this paper, we describe an alternative circuit design methodology when considering performance-accuracy-area tradeoffs. We suggest that for certain applications it is beneficial to move away from the traditional model of creating a conservative design that is guaranteed to avoid timing violations. Instead, it may be preferable to create a design in which timing violations may occur, under the knowledge that they only occur rarely because specific input patterns are required to generate the worst case errors. This paper elaborates on the prior work [xxx], by incorporating silicon area as another evaluation metric for the trade-offs. Based on this premise, we explicitly demonstrate the optimum design choice of the basic arithmetic operators (i.e. binary adders) under various design constraints. A summary of the main contributions of this work are as follows:

@@

\section{Background}\label{Section_Background}
\subsection{Word-length Optimization}\label{Section_Background_WL}
There exists a significant amount of work demonstrating that optimizing the precision used throughout the datapath would bring a substantial benefits on clock speed, silicon area and power consumption. As loosing precisions causes truncation or overflow errors, a main stream of research focus on analyzing errors generated from using the minimum precision and providing bounds of inputs to ensure the overall error are within the given accuracy specification. Current literatures report two major approaches in this area: the simulation-based approach [xxx] and the analytical-based approach including interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}. A detailed summary of these methods can be found in~\cite{GeorgeDT11, lee2006accuracy}.

\subsection{Imprecise Circuit Design Methodology}\label{Section_Background_Imprecise}
However, the choice of precision is not the only source of errors when designing a datapath. Recently we have seen a growth of parallel streams of research which aim at exploring alternative methods to trade accuracy for performance or energy efficiency. This strand of research is motivated by the fact that it becomes increasingly difficult and expensive to cover all possible worst cases when designing circuits, because the rapid scaling of technology introduces drastic variations on circuit performance.

@@

According to the existing literatures, one way to operating circuits beyond the deterministic region is to relax the design constraints and the guard-bands that are conventionally used to avoid the worst cases. Research in this area is based on the observations that in practice, the worst case happens rarely. A series of work known as ``Better-Than-Worst-Case (BTWC) Design'' introduced a universal framework to push the circuit performance to its limits~\cite{BetterThanWS2005}. In general, a BTWC design is composed of cores and checkers. The cores are operated with high performance by eliminating the conservative guard-bands, while the possible timing errors are diagnosed by the checkers. Optionally the system can be recovered at the observation of errors. As an exemplary design, the Razor project~\cite{Razor2003,Razor2004} was proposed to shave the conservative timing margins by overscaling the supply voltage and clock frequency, while monitoring the output error rates by utilizing a self-checking circuit. This work demonstrated that the benefits brought by removing the safe margin outweigh the cost of monitoring and recovering from errors. For example, $22\%$ or over $30\%$ power consumption can be saved with $\sim0.01\%$ or $\sim1\%$ error rates at the output, respectively. Related work includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA} or xxx.

Another key observation that has been made from existing work is that the worst-case normally happens with specific input patterns. Meanwhile, many studies have shown that errors can be potentially tolerated in various applications, e.g. DSP applications concerning human perceptions. In this case, an even greater performance/power benefits can be achieved, as the design overhead of the checkers can be eliminated. Current research in this area is focusing on designing ``probabilistic circuits'' that employ techniques from either software level or hardware level. For instance at the programming language level, a tool was proposed~\cite{EnerJ2011Uwash,Truffle2012Uwash} to divide the program into precise part and approximate part, both of which are mapped to different hardware with different speed-grades, supply voltages etc. This technique enables a relatively high service quality, in the meantime energy reduction can be obtained due to approximation. Similar ideas have also been applied on hardware directly. As an example, Palem et~al.~\cite{NonUniformScaling} described a non-uniform voltage scaling technique for the ripple carry adder. In this study, multiple voltage regions are employed for different bits along a carry chain. That is, higher voltage would be applied for computations generating most significant bits, and vice versa.

While the aforementioned literatures take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further to design a simplified circuit for peformance/energy efficiency. For example, Lu et~al. proposed a ``shrinking'' datapath that can be utilized to mimic and speculate the original logic functions~\cite{IntelSpeeding}. Kulkarni et.al. described an underdesigned $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straight-forward Karnaugh Map analysis~\cite{Undersigned2x2multiplier}. In this case, reduction of area and power consumption can be achieved with the cost of accuracy. In addition, Gupta et.al. developed approximate adders at the transistor level and compared the energy efficiency of their proposed architectures over truncation of input word-length of conventional structures~\cite{Gupta2013TransCADICS}.

However, the limitations of the existing work cannot be neglected. Firstly, some techniques, such as employing several voltages regions within a ripple carry adder, are not practical to achieve in real situations, and the overhead of applying this technique is not discussed. Secondly, many studies propose alternative architectures, which means the adaptability of this kind of technique is limited on current hardware platforms. Thirdly, the link between the probability of output correctness and energy savings or performance improvements are not analyzed.

@@

In our experiments, MRE is set ranging from $0.001\%$ to $50\%$. For a certain value of MRE, the design with the maximum operating frequency is selected as the optimum design. Moreover, the smallest design is the optimum one if multiple structures operate at the same frequency, with a certain area requirement. Fig.~\ref{Fig_CSA_Tradeoff_Error} can thus be obtained based on these criteria.
%Based on these criteria, the decision graph is depicted in
%We also notice that for small frequencies, RCA with either overclocking or truncation of word-length of the input signal is the best design choice for any area constraint, since
\begin{figure}[t]
    \centering
    \includegraphics[width=3.5in]{./Figures/Tradeoff_Error.eps}
    \caption{A demonstration of the optimum design methodology which runs at the fastest frequency with respect to a variety of accuracy and area constraints.}
    \label{Fig_CSA_Tradeoff_Error}
\end{figure}

@@

In this CCM structure, let the two inputs of the RCA be denoted by $A_S$ and $A_O$ respectively, which are both two's complement numbers. $A_S$ denotes the ``shifted signal", with zeros padded after LSB, while $A_O$ denotes the ``original signal" with MSB sign extension. For an $n$-bit input signal, it should be noted that an $n$-bit RCA is sufficient for this operation, because no carry will be generated or propagated when adding with zeros, as shown in Figure~\ref{CCM_fig}.
\begin{figure}[htbp]
  \centering
%  \vspace{-2ex}
  %\includegraphics[width=3.5in]{./Figures/CCM_DataFlow3.pdf}
  \includegraphics[width=3.3in]{./Figures/CCM_DataFlow3.eps}
%  \vspace{-2ex}
  \caption{Different types of carry chain in constant coefficient multiplier. The notion $s$ denotes the shifted bits and $BP$ denotes the binary point.}
  \label{CCM_fig}
%  \vspace{-1.5ex}
\end{figure}

@@

\section{Test Platform}\label{Experiment}
In our experiments, we compare two design perspectives. In the first scenario, the word-length of the input signal is truncated before propagating through the datapath in order to meet a given latency. In our proposed overclocking scenario, the circuit is overclocked while keeping the original operand word-length. The benefits of the proposed methodology are demonstrated over a set of DSP example designs, which are implemented on the Xilinx ML605 board with a Virtex-6 FPGA XC6VLX240T-1FFG1156.

@@

\section{Results and Discussion}\label{Section_Experiments}
\subsection{Case study: FIR filter}
We first assess the accuracy of our proposed models of error. The modeled values of both overclocking error and truncation error of the FIR filter are presented in Fig.~\ref{FIR} (dotted lines), as well as the actual measurements on the FPGA (solid lines) with two types of input data. The results demonstrate that our models match well with the practical results obtained using the uniform independent inputs.
% FIR
\begin{figure}[htbp]
  \centering
%  \vspace{-2.5ex}
  \includegraphics[width=3.5in]{./Figures/Exp/FIR/FIR_Error_New2.eps}
%  \vspace{-5ex}
  \caption{A demonstration of two design perspectives with a $5^{th}$~order FIR filter, which is implemented on Virtex-6 FPGA. The modeled values of both overclocking errors and truncation errors are presented as dotted lines. The actual FPGA measurements are depicted using solid lines. Two types of inputs are employed in the overclocking scenario: the uniformly distributed data and the real image data from Lena.}
  \label{FIR}
%  \vspace{-1ex}
\end{figure}

%Lena image
\begin{figure*}[htbp]
  %\vspace{-2ex}
  \centering
  \subfigure[425MHz,~n=8~,~no errors observed]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T8.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[430MHz,~n=8,~SNR=47.15dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T65.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=8,~SNR=24.1dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T62.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=8,~SNR=10.86dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T6.eps}
  \end{minipage}
  }\vspace{-1ex}
  \subfigure[425MHz,~n=7,~SNR=26.06dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q7T10.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[430MHz,~n=5,~SNR=24.85dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q4T10.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=2,~SNR=6.57dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q2T10.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=1,~SNR=3.95dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q1T10.eps}
  \end{minipage}
  }
%\vspace{-2ex}
\caption{Output images of the FIR filter for both overclocking scenario (top row) and traditional scenario (bottom row) under various operating frequencies.}
\label{FIR_Lena}
%\vspace{-2ex}
\end{figure*}

>>>>

\section{Introduction}
\IEEEPARstart{C}{ircuit} performance has increased tremendously over the past decades, with the continuous scaling of CMOS technology to the nanometer regime. However, the drastic variations introduced by higher integration densities is anticipated to be the major obstacle when designing reliable, high performance circuits. Although hardware designers traditionally employ safety margins to ensure a uniform functionality across a variety of possible working environments, there are two major problems if we keep using this approach nowadays. One is that the uniform performance should no longer be expected in the future, because the highly scaled CMOS devices would inevitably exhibit probabilistic or statistical behavior. The other problem is that covering all possible worst cases would become increasingly difficult, expensive and result in large yield loss because of the variation.

In addition, we also notice that the clock frequency is no longer scaling significantly with time, and the dark silicon becomes an important issue in circuit design since energy efficiency is considered to be the main limitation for performance improvement in embedded or mobile applications~\cite{FutureMicroprocessor2005,DarkSilicon2011}. In this case, designers tend to employ multi-core processors, heterogeneous systems and massive parallel accelerators to sustain the performance scaling.

Specifically, large volume of current studies has demonstrated that, significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications. However, one of the major factors that limits the performance of these accelerators is that they typically run at much lower clock frequencies than general purpose processors (GPPs) or GPUs. Furthermore, timing analysis tools typically report a very conservative clock frequency to guarantee ``safe'' operations. This substantially limits the potential performance of the device to a further extent.

In order to boost the operating frequency of a datapath, the standard approaches are either to heavily pipeline the design, or reduce the precision throughout the datapath. For the former method, it should be noted that pipelining will not tend to reduce the circuit latency. Actually the latency in terms of clock cycles will increase. As a result, this method will not be applicable to many embedded applications, which typically have strict latency requirements, or in datapath containing feedback where C-slow retiming is inappropriate. For the second approach, reducing the datapath precision would subtract out the latency, but at the cost of introducing quantization errors into the design. For hardware platforms such as FPGAs or ASICs, research into exploiting the potential benefits of using the minimum precision necessary to satisfy a design specification has been an extensive topic~\cite{GeorgeDT11}, as it is possible to use a number system with customized precisions on these platforms. A brief review of existing approaches in this area will be discussed in Section~\ref{Section_Background_WL}.

Unfortunately, neither of the conventional approaches tends to remove the conservative safety margin. In recent years, we have seen a growth of research that explores the potential power or performance benefits that can be obtained when relaxing the variation-induced guard-bands~\cite{NewBox2004}. The detailed review of this research field will be presented in Section~\ref{Section_Background_Imprecise}.

In this paper, we describe an alternative circuit design methodology when considering tradeoffs between accuracy, performance and area. We suggest that for certain applications it is beneficial to move away from the traditional model of creating a conservative design that is guaranteed to avoid timing violations. Instead, it may be preferable to create a design in which timing violations may occur, under the knowledge that they only occur rarely because specific input patterns are required to generate the worst case errors. This paper elaborates on the prior work [xxx], with a further enrichment by incorporating silicon area as another evaluation metric for the trade-offs. In this work, we explicitly demonstrate the optimum design choice of the basic arithmetic operators (i.e. binary adders) under various design constraints. A summary of the main contributions of this work are as follows:

@@

\section{Background}\label{Section_Background}
\subsection{Word-length Optimization}\label{Section_Background_WL}
There exists a significant amount of work demonstrating that optimizing the precision used throughout the datapath would bring a substantial benefits on clock speed, silicon area and power consumption. As loosing precisions causes truncation or overflow errors, a main stream of research focus on analyzing errors generated from using the minimum precision and providing bounds of inputs to ensure the overall error are within the given accuracy specification. Current literatures report two major approaches in this area: the simulation-based approach [xxx] and the analytical-based approach such as interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}. A detailed summary of these methods can be found in~\cite{GeorgeDT11, lee2006accuracy}.

\subsection{Imprecise Circuit Design Methodology}\label{Section_Background_Imprecise}
Note that, however, the choice of precision is not the only source of errors when designing a datapath. Recently we have seen a growth of parallel streams of research which aim at exploring alternative methods to trade accuracy for design efficiency. This strand of research is motivated by the drastic performance variations introduced by process scaling.

%it becomes increasingly difficult and expensive to cover all possible worst cases when designing circuits, because the rapid scaling of technology introduces drastic variations on circuit performance.

@@

According to the existing literatures, one way to operating circuits beyond the deterministic region is to relax the design constraints and the guard-bands that are conventionally used to avoid the worst cases. Research in this area is based on the observations that in practice, the worst case happens rarely. A series of work known as ``Better-Than-Worst-Case (BTWC) Design'' introduced a universal framework to push the circuit performance to its limits~\cite{BetterThanWS2005}. In general, a BTWC design is composed of cores and checkers. The cores are operated with high performance by eliminating the guard-bands, meanwhile the possible timing errors are diagnosed by the checkers. Optionally the system can be recovered at the observation of errors. As an exemplary design, the Razor project~\cite{Razor2003,Razor2004} was proposed to shave the conservative timing margins by overscaling the supply voltage and clock frequency, while monitoring the output error rates by utilizing a self-checking circuit. This work demonstrated that the benefits brought by removing the safe margin outweigh the cost of monitoring and recovering from errors. For example, $22\%$ or over $30\%$ power consumption can be saved with $\sim0.01\%$ or $\sim1\%$ error rates at the output, respectively. Related work includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA} or xxx.

Another key observation that has been made from existing work is that the worst-case normally happens with specific input patterns. Meanwhile, many studies have shown that errors can be potentially tolerated in various applications, e.g. DSP applications concerning human perceptions. In this case, an even greater performance/power benefits can be achieved, as the design overhead of the checkers can be eliminated. Current research in this area is focusing on designing probabilistic or imprecise circuits that employ techniques from either software level or hardware level. For instance at the programming language level, a tool was proposed~\cite{EnerJ2011Uwash,Truffle2012Uwash} to divide the program into the precise parts and the approximate parts, both of which are mapped to different hardware with different speed-grades, supply voltages etc. This technique enables a relatively high service quality, in the meantime energy reduction can be obtained due to approximation. Similar ideas have also been applied on hardware directly. As an example, Palem et~al.~\cite{NonUniformScaling} described a non-uniform voltage scaling technique for the ripple carry adder. In this study, multiple voltage regions are employed for different bits along a carry chain. That is, higher voltage would be applied for computations generating most significant bits, and vice versa.

While the aforementioned literatures take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further by designing simplified circuits for peformance/energy efficiency. For example, Lu et~al. proposed a ``shrinking'' datapath that can be utilized to mimic and speculate the original logic functions~\cite{IntelSpeeding}. Kulkarni et.al. described an underdesigned $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straight-forward Karnaugh Map analysis~\cite{Undersigned2x2multiplier}. In both cases, reduction of area and power consumption can be achieved with the cost of accuracy. In addition, Gupta et.al. developed approximate adders at the transistor level and compared the energy efficiency of their proposed architectures over truncation of input word-length of conventional structures~\cite{Gupta2013TransCADICS}.

However, the limitations of the existing work should not be neglected. Firstly, some techniques, such as employing several voltages regions within a ripple carry adder, are not practical to achieve in real situations, and the overhead of applying this technique is not discussed. Secondly, many studies propose alternative architectures, which means the adaptability of this kind of technique is limited on current hardware platforms. More importantly, correct results would never be obtained by using approximate architectures. Thirdly, the link between the probability of output correctness and energy savings or performance improvements are rarely analyzed from current research.

@@

In our experiments, MRE is set ranging from $0.001\%$ to $50\%$. For a certain value of MRE, the design with the maximum operating frequency is selected as the optimum design. Moreover, the smallest design is the optimum one if multiple structures operate at the same frequency, with a certain area requirement. Fig.~\ref{Fig_CSA_Tradeoff_Error} can thus be obtained based on these criteria.
%Based on these criteria, the decision graph is depicted in
%We also notice that for small frequencies, RCA with either overclocking or truncation of word-length of the input signal is the best design choice for any area constraint, since
\begin{figure}[t]
    \centering
    \includegraphics[width=3.7in]{./Figures/Tradeoff_Error.eps}
    \caption{A demonstration of the optimum design methodology which runs at the fastest frequency with respect to a variety of accuracy and area constraints.}
    \label{Fig_CSA_Tradeoff_Error}
\end{figure}

@@

In this CCM structure, let the two inputs of the RCA be denoted by $A_S$ and $A_O$ respectively, which are both two's complement numbers. $A_S$ denotes the ``shifted signal", with zeros padded after LSB, while $A_O$ denotes the ``original signal" with MSB sign extension. For an $n$-bit input signal, it should be noted that an $n$-bit RCA is sufficient for this operation, because no carry will be generated or propagated when adding with zeros, as shown in Fig.~\ref{CCM_fig}.
\begin{figure*}[htbp]
  \centering
  \includegraphics[width=0.99\textwidth]{./Figures/CCM_CarryChain.pdf}
  \caption{Four possible carry chain types in a constant coefficient multiplier with $n$-bit inputs. The notion $s$ denotes the shifted bits and $BP$ denotes the binary point.}
  \label{CCM_fig}
\end{figure*}

@@

\section{Test Platform}\label{Experiment}
In our experiments, we compare two design perspectives. In the first scenario, the word-length of the input signal is truncated before propagating through the datapath in order to meet a given latency. In our proposed overclocking scenario, the circuit is overclocked while keeping the original operand word-length. The benefits of the proposed methodology are demonstrated over a set of DSP example designs, which are implemented on the Xilinx ML605 board with a Virtex-6 FPGA. 
%XC6VLX240T-1FFG1156.

@@

\section{Results and Discussion}\label{Section_Experiments}
\subsection{Case study: FIR filter}
We first assess the accuracy of our proposed models of error. The modeled values of both overclocking error and truncation error of the FIR filter are presented in Fig.~\ref{FIR} (dotted lines), as well as the actual measurements on the FPGA (solid lines) with two types of input data. The results demonstrate that our models match well with the practical results obtained using the uniform independent inputs.
% FIR
\begin{figure}[htbp]
  \centering
%  \vspace{-2.5ex}
  \includegraphics[width=3.5in]{./Figures/Exp/FIR/FIR_Error_New_TCAD.eps}
%  \vspace{-5ex}
  \caption{A demonstration of two design perspectives with a $5^{th}$~order FIR filter, which is implemented on Virtex-6 FPGA. The modeled values of both overclocking errors and truncation errors are presented as dotted lines. The actual FPGA measurements are depicted using solid lines. Two types of inputs are employed in the overclocking scenario: the uniformly distributed data and the real image data from Lena.}
  \label{FIR}
%  \vspace{-1ex}
\end{figure}

%Lena image
\begin{figure*}[htbp]
  %\vspace{-2ex}
  \centering
  \subfigure[425MHz,~n=8~,~SNR=47.97dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T8.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[450MHz,~n=8,~SNR=44.94dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T65.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=8,~SNR=21.58dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T62.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=8,~SNR=10.03dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T6.eps}
  \end{minipage}
  }\vspace{-1ex}
  \subfigure[425MHz,~n=7,~SNR=26.02dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q7T10.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[450MHz,~n=5,~SNR=21.76dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q4T10.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=2,~SNR=6.57dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q2T10.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=1,~SNR=3.95dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q1T10.eps}
  \end{minipage}
  }
%\vspace{-2ex}
\caption{Output images of the FIR filter for both overclocking scenario (top row) and traditional scenario (bottom row) under various operating frequencies.}
\label{FIR_Lena}
%\vspace{-2ex}
\end{figure*}
